Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-08-13 paper/snakemajoranas.tex
add part with boundary modulation

% \begin{figure}[!htb]
% \centering
% \includegraphics[width=0.9\columnwidth]{figures/bandstructure_of_small_period_zigzag.pdf}
% \caption{The effect of increased transparency.
% % Like Fig 2. (b) plus horizontal dashed lines indicating the gap of zigzag and straight junctions
% \label{fig:bandstructure_of_small_period_zigzag}}
% \end{figure}

>>>>

To verify that the change in the interface transparency alone is not sufficient to explain the increase of the topological gap, we have simulated the dispersion of a system with $z_x = z_y = \SI{80}{\nm} \approx v_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
We have observed that $E_\textrm{gap}$ became $\SI{6.1}{\mu \eV}$, a 2x increase compared to the straight system.
